---
params:
  country: ""
title: '<span style="color:red;">DRAFT</span> Mapping Behavioral Risk Data: `r params$country`'
date: "`r Sys.Date()`"
output:
  html_document:
    keep_md: false
    theme: readable
    toc: true
    toc_float: true
    highlight: pygments
---

```{r setup, include=FALSE}

purrr::walk(list.files(here::here("R/"), full.names = TRUE),
            source, echo = FALSE, verbose = FALSE)

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, error = FALSE, out.extra = '')
country <- params$country

# Read in data
dat <- read_csv(h(paste0("data/raw-behav-", country, ".csv")), col_types = cols()) 

# Get Site names
site_names <- read_csv(h(paste0("data/site-name-formatted-", country, ".csv")), col_types = cols())

# Cleaning
fdat <- dat %>% 
  left_join(site_names, by = c("country" = "country", "concurrent_sampling_site" = "old")) %>%
  group_by(concurrent_sampling_site) %>% 
  mutate(site_latitude = mean(site_latitude), 
         site_longitude = mean(site_longitude),
         site_name = gsub(" ", "-", tolower(concurrent_sampling_site))) %>%  # take average to handle some inconsistencies
  ungroup() %>%
  rename(hovertext = new)

```

```{r get-adm, include=FALSE}
# Get administrative borders of countries of interest
country_wrld <- str_replace(country, "\\-.*", "")
country_wrld <- str_replace(country, "^DR", "Democratic Republic of the")
country_wrld <- str_replace(country, "PDR", "People's Democratic Republic")

data(wrld_simpl)
admin <- wrld_simpl[wrld_simpl@data$NAME %in% country_wrld, ]

```

## Data Description 

These maps display data collected from questionnaires and interviews conducted by USAID's PREDICT project. These data were collected by the behavioral risk team and are related to knowledge, behaviors, and skills that are suspected to increase or reduce the risk of contracting a zoonotic viral disease. 

Study sites were selected by PREDICT as priority surveillance sites with high risk for viral spillover, evolution, amplification, and spread (i.e., ‘hotspots’).  PREDICT study sites are prioritized by identifying areas considered high-risk for contact with multiple taxonomic groups known to be associated with zoonotic viral diversity and with ecological and epidemiological conditions associated with disease emergence. 

This report is generated using current site data from PREDICT's secure [EIDITH](http://eidith.org) database via the EIDITH [R package](http://github.com/ecohealthalliance/eidith). Within individual countries, some of this data may be incomplete. 


## Questionnaires completed at each site

Hover over sites for the name of each study site and the number of questionnaires completed in each site. 
```{r map-questionnaires}

quest <- fdat %>%
  select(country, site_latitude, site_longitude, full_site_name, site_name, concurrent_sampling_site, n, hovertext) %>% 
  unique()

# Set color palette 
# bins <- seq(min(quest$n), max(quest$n), length.out = 7) %>% round() %>% unique()
# pal <- leaflet::colorBin(palette = RColorBrewer::brewer.pal(9, "Reds")[3:9], domain = quest$n, 
#                          na.color = "transparent", bins = bins)
pal <- colorNumeric(palette = "Reds", domain = quest$n)
if(nrow(quest)==1){
  pal <- colorFactor(palette = "Spectral", domain = quest$n)
}

# Map  
leaflet(quest) %>%
  setView(lng = mean(quest$site_longitude), lat = mean(quest$site_latitude)-10, zoom = 3) %>%
  addProviderTiles("OpenStreetMap.Mapnik") %>% 
  addCircleMarkers( lng = ~site_longitude, lat = ~site_latitude, color = "#000000", weight = 0.5,  
                    opacity = 100, radius = ~log(n) * 5, 
                    fillColor = ~pal(n), 
                    fillOpacity = 0.5,
                    label = ~hovertext,
                    labelOptions = lapply(1:nrow(quest), function(x) {
                      labelOptions(direction='auto') })) %>%    
  addPolygons(
    data = admin, opacity = 100,
    color = "#000000",
    weight = 1, 
    options = list(clickable = FALSE),
    fill = F, 
    highlightOptions = highlightOptions(weight = 3, bringToFront = TRUE)) %>%
  addLegend_decreasing("bottomleft", pal = pal, values = ~n, decreasing = TRUE,
                       title = "Questionnaires conducted",
                       opacity = 1) 

```

```{r table-questionnaires}
quest %>%
  arrange(-n) %>%
  select(site = full_site_name, n)  %>%
  datatable(., rownames = FALSE,
            options = list(pageLength = Inf)) %>%
  formatStyle(c(1:3), `font-size` = '12px')

```

## Age pyramids in each study site

Click on study sites for the age and gender breakdown of questionnaire respondants. 
```{r get-age-dat}
age <-  fdat %>%
  mutate(gender = na_if(gender, "other")) %>%
  drop_na(age, gender) %>%
  mutate( agebrack = cut(as.integer(age), breaks=c(0, 10, 20, 30, 40, 50, 60, 70, Inf),
                         labels = c("under 10", "10 - 19", "20 - 29", "30 - 39",
                                    "40 - 49", "50 - 59", "60 - 69", "70 +"), right = FALSE),
          age_pngpath = paste0(h("outputs/age-figs/"), country, "-", site_name, "-age-dist.png"))

```

```{r gen-age-plots, message = FALSE}
age_split <- split(age, age$full_site_name)

pal <- c(male = viridis::viridis_pal()(3)[1], 
         female = viridis::viridis_pal()(3)[2], 
         other = viridis::viridis_pal()(3)[3])

iwalk(age_split, function(x, y){
  
  title <- paste0("Age distribution by gender in \n", y)
  path <- unique(x$age_pngpath)
  
  p <- ggplot(x, aes(x = agebrack, y = ifelse(gender == "male",-1, 1), fill = gender)) + 
    geom_col() + 
    scale_y_continuous(labels = abs) +
    theme_fivethirtyeight() +
    #theme_avenir(base_family = "Avenir") + 
    coord_flip() +
    labs(x = "age group", y = "count", title = title) + 
    scale_fill_manual(values = pal) +
    theme(axis.title = element_text()) +
    theme(legend.position = "right", legend.direction = "vertical")
  
  ggsave(filename = path, plot = p, width = 8, height = 6)
  
})

```


```{r map-age-plots}
age_map <- age %>%
  select(country, full_site_name, site_latitude, site_longitude, n, age_pngpath) %>% 
  distinct() 

age_popup <- map(1:nrow(age_map), ~popup_image_mod(age_map$age_pngpath[[.]])) %>% unlist()

leaflet(age_map) %>%
  setView(lng = mean(age_map$site_longitude), lat = mean(age_map$site_latitude)-10, zoom = 3) %>% 
  addProviderTiles("OpenStreetMap.Mapnik") %>% 
  addCircleMarkers( 
    data = age_map, lng = age_map$site_longitude, lat = age_map$site_latitude, color = "black", opacity = 1, weight = 1,
    popup =  age_popup) %>%
  addPolygons(
    data = admin, opacity = 100,
    color = "#000000",
    weight = 1, popup = NULL,
    options = list(clickable = FALSE),
    fill = F) 

```

## Lifetime and Annual hunting prevalence

Hover over sites for proportions and total numbers of respondents who responded that they had hunted.

```{r get-hunt-dat, include=FALSE}

# Proportions of people who have hunted in the last year and ever by site
hunt <- fdat %>%
  mutate_at(.vars = c("hunted_animal_life", "hunted_animal_last_year"),
            ~recode(., "yes" = 1, "no" = 0, "missing" = NA_real_, "N/A" = 0)) %>%
  group_by(country, full_site_name, site_longitude, site_latitude, n) %>%
  summarize(life = sum(hunted_animal_life, na.rm = T),
            year = sum(hunted_animal_last_year, na.rm = T),
            life_prop = sum(hunted_animal_life, na.rm = T)/n(),
            year_prop = sum(hunted_animal_last_year, na.rm = T)/n()) %>%
  mutate(life_perc = scales::percent(life_prop),
         year_perc = scales::percent(year_prop)) %>%
  mutate(lifelab = paste0(full_site_name, ": ", life_perc, " (", life, "/", n, " respondents)"),
         yearlab = paste0(full_site_name, ": ", year_perc, " (", year, "/", n, " respondents)"))

```

```{r map-hunt}
# Set color palette
bins <- seq(0, 1, by = .2)
pal_life <- leaflet::colorBin(palette = scales::brewer_pal(palette = "YlOrBr")(5),
                              domain = hunt$life_prop, na.color = "transparent", bins = bins)
pal_year<- leaflet::colorBin(palette = scales::brewer_pal(palette = "YlOrBr")(5),
                             domain = hunt$year_prop, na.color = "transparent", bins = bins)

# map hunting
leaflet(hunt) %>%
  setView(lng = mean(hunt$site_longitude), lat = mean(hunt$site_latitude)-10, zoom = 4) %>%
  addProviderTiles("OpenStreetMap.Mapnik") %>%
  addCircleMarkers(
    lng = ~site_longitude, lat = ~site_latitude,
    color = "#b2b2b2", weight = 1, opacity = 100,
    radius = ~log(n)*3, fillColor = "#b2b2b2", fillOpacity = 0.2,
    group = "All Respondents") %>%
  addCircleMarkers(
    lng = ~site_longitude, lat = ~site_latitude, color = "#000000", weight = 1, opacity = 100,
    fillColor = ~pal_life(life_prop),
    radius = ~log(life)*3,
    fillOpacity = 0.8,
    #clusterOptions = markerClusterOptions(),
    group = "Ever Hunted",
    label = ~lifelab) %>%
  addCircleMarkers(
    lng = ~site_longitude, lat = ~site_latitude, color = "#000000", weight = 1, opacity = 100,
    radius = ~log(year)*3,
    fillColor = ~pal_year(year_prop), fillOpacity = 0.8,
    #clusterOptions = markerClusterOptions(),
    group = "Hunted This Year",
    label = ~yearlab) %>%
  addLayersControl(position = "bottomright",
                   overlayGroups = c("All Respondents", "Ever Hunted", "Hunted This Year"),
                   options = layersControlOptions(collapsed = FALSE)
  ) %>%
  addLegend("bottomleft", pal = pal_year, values = ~life, title = "% respondents in study site",
            opacity = 1)

```

## Hunting by Site

```{r table-hunt}
hunt %>%
  group_by(full_site_name) %>%
  select(site = full_site_name,
         "n" = `n`,
         "ever hunted" = life,
         "% ever hunted" = life_perc,
         "hunted last year" = year,
         "% hunted last year" = year_perc
  ) %>%
  arrange(desc(`n`)) %>%
  DT::datatable(., rownames = FALSE)

```

## Animal-related Risk Behaviors

Several questions asked about behaviors that lead to increased contact with animals. Some of these behaviors could indicate an increased risk of contracting a zoonotic disease.

They are as follows:

39. Has an animal lived as a pet in or near your dwelling?
40. Have you handled live animals?
41. Have you raised live animals?
42. Have you shared a water source with animals for washing? (yes/no/don't know)
43. Have you seen animal feces in or near food before you have eaten it?
44. Have you eaten food after an animal has touched or damaged it? For example, chew marks or scratches (yes/no/don't know)
45. Do any animals come inside the dwelling where you live?
46. Have you cooked or handled meat, organs or blood from a recently killed animal?
47. Have you eaten raw or undercooked meat or organs or blood?
48. Have you eaten an animal that you knew was not well/sick? (yes/no/don't know)
49. Have you found a dead animal and collected it to eat or share?
50. Have you found a dead animal and collected it to sell it?
51. Have you been scratched or bitten by an animal?
52. Have you hunted or trapped an animal?
53. Have you slaughtered an animal?


```{r get-contact-dat}

# Get var names
vec <- c(which(names(fdat) == "pet_in_dwelling_life"):which(names(fdat) == "slaughtered_animal_last_year"))
cnames <- c("ID", "country", "site_latitude", "site_longitude", "full_site_name", "site_name", "n",  names(fdat[vec]))

# Joining the vars with the actual typed out questions
contact_names <- tibble(variable = c("animals_in_dwelling", "animal_feces_food",
                                     "handle_animals", "pet_in_dwelling",
                                     "raised_animals", "cooked_meat",
                                     "shared_water", "animals_in_food",
                                     "slaughtered_animal", "eaten_sick_animal",
                                     "eaten_raw_meat", "eaten_dead_animal",
                                     "hunted_animal", "scratched_bitten",
                                     "sold_dead_animal"),
                        question = c("Do any animals come inside the dwelling where you live?",
                                     "Have you seen animal feces in or near food before you have eaten it?",
                                     "Have you handled live animals?",
                                     "Has an animal lived as a pet in or near your dwelling?",
                                     "Have you raised live animals?",
                                     "Have you cooked or handled meat, organs or blood from a recently killed animal?",
                                     "Have you shared a water source with animals for washing?",
                                     "Have you eaten food after an animal has touched or damaged it?",
                                     "Have you slaughtered an animal?",
                                     "Have you eaten an animal that you knew was not well /sick?",
                                     "Have you eaten raw or undercooked meat or organs or blood?",
                                     "Have you found a dead animal and collected it to eat or share?",
                                     "Have you hunted or trapped an animal?",
                                     "Have you been scratched or bitten by an animal?",
                                     "Have you found a dead animal and collected it to sell it?"))

# Spread, mutate, and gather the risk questions
contact <- fdat %>%
  #as.data.frame() %>%
  mutate(ID = row_number()) %>%
  dplyr::select(cnames) %>%
  gather(-c(ID:n), key = "variable", value = "value") %>%
  mutate(time_period = str_extract(variable, "life|last_year"),
         variable = str_remove(variable, "_life|_last_year")) %>%
  spread(time_period, value) %>%
  mutate(last_year = ifelse(life == "don't know", "don't know", last_year),  #if life is unknown, so is last_year
         last_year = ifelse(last_year == "N/A", "no", last_year),
         last_year = na_if(last_year, "don't know"),
         last_year = na_if(last_year, "missing"),
         last_year = recode(last_year, "yes" = 1, "no" = 0)) %>%
  group_by(country, full_site_name, site_name, variable, site_latitude, site_longitude, n) %>%
  summarise(last_year = sum(last_year, na.rm = TRUE),
            last_year_prop = sum(last_year, na.rm = TRUE)/n()) %>%
  ungroup() %>%
  left_join(., contact_names, by = "variable") %>%
  mutate(contact_pngpath = paste0(h("outputs/animal-contact-figs/"), country, "-", site_name, "-animal-contact.png"))

```

```{r gen-contact-plots, message = FALSE}
contact_split <- split(contact, contact$full_site_name)

iwalk(contact_split, function(x, y){
  
  title <- paste0("Prevalance of animal-related behaviors in the last year in ", y)
  cap <- paste0("Based on questionnaire responses from ", unique(x$n), " individuals")
  path <- unique(x$contact_pngpath)
  
  p <- ggplot(x, aes(x = reorder(question, last_year_prop), y = last_year_prop,
                     fill = reorder(question, last_year_prop))) +
    geom_col() +
    geom_text(aes(label = scales::percent(last_year_prop)), size = 15, hjust = -0.25) +
    theme_fivethirtyeight() +
    coord_flip() +
    ylim(0, 1) +
    labs(x = NULL, 
         y = "proportion of respondents answering `yes`", 
         title = title,
         caption = cap) +
    scale_fill_manual(values = rev(viridis::viridis_pal()(15))) +
    theme(text = element_text(size = 40), 
          axis.text.y = element_text(size = 55),
          axis.text.x = element_blank(),
          plot.title = element_text(hjust=1),
          plot.subtitle = element_text(hjust=-3)) +
    guides(fill = F) 
  
  
  ggsave(filename = path, plot = p, width = 45, height = 20 )
})
```

Prevalence of these behaviors varies greatly by site. The map below shows similar frequencies of behaviors over the past year in each study site. This data was collected between `r min(dat$date_of_interview)` and `r max(dat$date_of_interview)`.

```{r map-contact}
contact_map <- contact %>%
  select(country, full_site_name, site_latitude, site_longitude,  contact_pngpath) %>%
  distinct()

# may need to try this to get image size working: https://stackoverflow.com/questions/53523494/control-the-size-of-popupimage-from-leaflet-in-r-shiny
contact_popup <- map(1:nrow(contact_map), ~popup_image_mod(contact_map$contact_pngpath[[.]])) %>% unlist()

leaflet(contact_map) %>%
  setView(lng = mean(contact_map$site_longitude), lat = mean(contact_map$site_latitude)-10, zoom = 3) %>%
  addProviderTiles("OpenStreetMap.Mapnik") %>%
  addCircleMarkers(
    data = contact_map, lng = ~site_longitude, lat = ~site_latitude, color = "black", opacity = 1, weight = 1,
    popup = contact_popup) %>%
  addPolygons(
    data = admin, opacity = 100,
    color = "#000000",
    weight = 1, popup = NULL,
    options = list(clickable = FALSE),
    fill = F)


```


```{r get-taxa-dat}
taxa_cols <- c("nhp_contact", "bats_contact", "rodents_contact")
animals <- c("non-human primates", "bats", "rodents")
names(animals) <- taxa_cols

taxa <- map_df(taxa_cols, function(x){
  fdat %>%
    eidith::ed2_expand_long(., !!sym(x), other_details = TRUE) %>%
    group_by(country, full_site_name, site_name, n, site_latitude, site_longitude, !!sym(paste0(x, "_val"))) %>%
    count() %>%
    ungroup() %>%
    mutate(prop = nn/n, taxa = animals[[x]]) %>%
    rename(contact_type = !!sym(paste0(x, "_val"))) %>%
    filter(!is.na(contact_type)) %>%
    mutate(taxa_pngpath = paste0(h("outputs/animal-contact-figs/"), str_replace(taxa, " ", "-"), "/", country, "-", site_name, "-", str_replace(taxa, " ", "-"),  "-contact.png"))
})
```

```{r gen-taxa-plots, message = FALSE}
taxa$split <- paste(taxa$full_site_name, taxa$taxa, sep = " - ")
taxa_split <- split(taxa, taxa$split)

iwalk(taxa_split, function(x, y){
  
  tx <- unique(x$taxa)
  fs <- unique(x$full_site_name)
  
  title <- paste0("Contact with ", tx , " in \n", fs)
  cap <- paste0("Based on questionnaire responses from ", unique(x$n), " individuals")
  path <- unique(x$taxa_pngpath)
  
  
  ggplot(x, aes(x = reorder(contact_type, prop), y = prop,
                fill = reorder(contact_type, prop))) +
    geom_col() +
    theme_fivethirtyeight() +
    coord_flip() +
    ggtitle(title) +
    ylim(0, 1) +
    labs(x = NULL, y = "proportion of respondents who had each kind of contact", caption = cap) +
    scale_fill_manual(values = rev(viridis::viridis_pal()(12))) +
    geom_text(aes(label = scales::percent(prop)), size = 3, hjust = -0.25) +
    guides(fill = F)
  ggsave(filename = path, width = 7, height = 5)
  
})
```


## Contact patterns by taxa

The following map breaks down the various risk-related behaviors and contact patterns by the three primary taxa of interest - rodents, bats, and non-human primates.

In the next map, zoom into a cluster to show the sites in that location. Click on a taxa icon to display the frequencies of various kinds of interactions. Click and unclick taxa layers in the bottom left corner to display or hide that taxa.

```{r, map-taxa}

taxa_map <- taxa %>%
  select(country, full_site_name,  site_latitude, site_longitude, n, taxa, taxa_pngpath) %>%
  distinct() %>%
  mutate(taxa_pngpath = map(taxa_pngpath, ~popup_image_mod(.))) %>%
  spread(key = taxa, value = taxa_pngpath)

# define icons
primate <- makeIcon(
  iconUrl = h("assets/primate.png"),
  iconWidth = 50, iconHeight = 46,
  iconAnchorX = 25, iconAnchorY = 45
)

bat <- makeIcon(
  iconUrl = h("assets/bat.png"),
  iconWidth = 50, iconHeight = 37,
  iconAnchorX = 35, iconAnchorY = 36
)

rodent <- makeIcon(
  iconUrl = h("assets/rodent.png"),
  iconWidth = 50, iconHeight = 25,
  iconAnchorX = 25, iconAnchorY = 24
)

taxa_leaflet <- leaflet(taxa_map) %>%
  setView(lng = mean(taxa_map$site_longitude), lat = mean(taxa_map$site_latitude), zoom = 4) %>%
  addProviderTiles("OpenStreetMap.Mapnik") %>%
  addLayersControl(position = "bottomleft",
                   overlayGroups = c("Non-Human Primates", "Bats", "Rodents"),
                   options = layersControlOptions(collapsed = FALSE)) %>%
  addPolygons(
    data = admin, opacity = 100,
    color = "#000000",
    weight = 1, popup = NULL,
    options = list(clickable = FALSE),
    fill = F)

if("non-human primates" %in% colnames(taxa_map)){
  taxa_leaflet <- taxa_leaflet %>%
    addMarkers(lng = ~(site_longitude+.05), lat = ~site_latitude, icon = primate, popup = ~`non-human primates`,
               clusterOptions = markerClusterOptions(),
               group = "Non-Human Primates") 
}

if("bats" %in% colnames(taxa_map)){
  taxa_leaflet <- taxa_leaflet %>%
    addMarkers(lng = ~(site_longitude-.05), lat = ~site_latitude, icon = bat,  popup = ~bats,
               clusterOptions = markerClusterOptions(),
               group = "Bats") 
}

if("rodents" %in% colnames(taxa_map)){
  taxa_leaflet <- taxa_leaflet %>%
    addMarkers(lng = ~site_longitude, lat = ~(site_latitude-.04), icon = rodent,  popup = ~rodents,
               clusterOptions = markerClusterOptions(),
               group = "Rodents") 
}

taxa_leaflet

```
